Agents and you, a brief summary

### 2015-12-02 methods/agents/summery.tex
added context logic

\subsubsection{Doxastic rules}
\begin{itemize}
	\item Propositional calculus (including modus ponens)
	\item $(B\phi \wedge B(\phi \to \psi)) \to B \phi$ (B axiom)
	\item $\frac{\phi}{B\phi}$ (necisitation rule)
	\item $\neg B \bot$ (belief is consistent)
	\item $B \phi \to BB\phi$ (positive introspection)
	\item $\neg B \phi \to B\neg B\phi$ (negative introspection)
\end{itemize}
\section{APL}
Medhi dastani taught about the agent programming langauge (APL).
\subsection{Agent data structure}
This represents the mental state of a agent. \\
\begin{tabular}{ll}
	Name & Does what \\ \toprule
	Beliefs & Information available to the agent \\
	Goals & Objectives that the agent wants to achieve \\
	Events & Obsevations of (environmental) changes \\
	Capabilities & Actions that the agent can perform \\
	Plans & Procedures to achieve objectives \\
	Reasoning rules & Reason about goal and plans \\
\end{tabular} \\

>>>>

\subsubsection{Doxastic rules}
\begin{itemize}
	\item Propositional calculus (including modus ponens)
	\item $(B\phi \wedge B(\phi \to \psi)) \to B \phi$ (B axiom)
	\item $\frac{\phi}{B\phi}$ (necisitation rule)
	\item $\neg B \bot$ (belief is consistent)
	\item $B \phi \to BB\phi$ (positive introspection)
	\item $\neg B \phi \to B\neg B\phi$ (negative introspection)
\end{itemize}

\subsection{ContextLogic: $S5P,K45^{ij}$}

\paragraph{Universal modality $\Box$} Based on S5(equivalence relation).
\paragraph{Cluster modality [i]} referring to subrelations ('clusters') of
universal relation. Its Transative, euclidean $K45$

\subsubsection{S5P Models}
\[M (S,\pi, S_1, S_2, \dots, S_n\]
\begin{tikzpicture}
    \draw (0,0) ellipse (5cm and 3cm);
	\draw[color=red] (1,1) ellipse (2cm and 1cm);
    \draw[color=red] (0,1) ellipse (2cm and 1cm);
    \draw[color=red] (0,0) ellipse (2cm and 1cm);
    \draw[color=red] (-1,-2) ellipse (2cm and 0.5cm);
\end{tikzpicture}

\subsubsection{Semantics}
\begin{tabular}{lll}
	Modal & $\Leftrightarrow$ & Interpertation \\ \toprule
	$M,s \vDash \Box\phi$ & $\Leftrightarrow$ &
	$M,s' \vDash \phi$ for all $s'$ $\in S$ \\

	$M,s \vDash [i]\phi$ & $\Leftrightarrow$ &
	$M,s' \vDash \phi $ for all $s'$ $\in S_i$ \\

	$M,s \vDash \Box\phi$ & $\Leftrightarrow$ &
	$M,s' \vDash \phi $ for all $s'$ $\in S$ such that $R(s,s')$ \\

	$M,s \vDash [i]\phi$ & $\Leftrightarrow$ &
	$M,s' \vDash \phi $ for all $s'$ $\in S_i$ such that $R_i(s,s')$ \\
\end{tabular}

\paragraph{Accessibility relations}
\[R(s,s') \mbox{ for all } s,s' \in S\]
\[R_i(s,s') \mbox{ for all } s,s' \in S_i\]

$R$ is equivalance and $R_i$ is transative and euclidean.

\[S5P = K45^{ij}_{(m)} + \Box\]

\section{APL}
Medhi dastani taught about the agent programming langauge (APL).
\subsection{Agent data structure}
This represents the mental state of a agent. \\
\begin{tabular}{ll}
	Name & Does what \\ \toprule
	Beliefs & Information available to the agent \\
	Goals & Objectives that the agent wants to achieve \\
	Events & Obsevations of (environmental) changes \\
	Capabilities & Actions that the agent can perform \\
	Plans & Procedures to achieve objectives \\
	Reasoning rules & Reason about goal and plans \\
\end{tabular} \\
